A hybrid approach for news recommender system using optimization methods

### 2021-01-09 paper/paper.tex
added input data section

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		    % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{enumitem}       % itemize settings
\usepackage{cleveref}       % reference section with capital letter
\usepackage{xcolor}         % additional colors for hypersetup

\setlist[itemize]{noitemsep, topsep=0pt} % no space between itemize

\hypersetup{
    colorlinks=true,
    citecolor=violet,
    linkcolor=violet,
    filecolor=violet,      
    urlcolor=black,
}

@@

@@

>>>>

\usepackage{fontspec}                % font for emoji
\newfontfamily\DejaSans{DejaVu Sans}

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		    % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}            % hyperlink to doi.org
\usepackage{enumitem}       % itemize settings
\usepackage{cleveref}       % reference section with capital letter
\usepackage{xcolor}         % additional colors for hypersetup
\usepackage{booktabs}       % beauful tables
\usepackage{caption}        % table caption margin
\usepackage{placeins}       % floatbarrier

\captionsetup[table]{skip=10pt}          % table caption margin
\setlist[itemize]{noitemsep, topsep=0pt} % no space between itemize
\hypersetup{
    colorlinks=true,
    citecolor=violet,
    linkcolor=violet,
    filecolor=violet,      
    urlcolor=black,
}

@@

    As we solving domain specific task, we have domain specific data.

    \subsection*{metadata}

    \begin{table}[h]
        \centering
        % \resizebox{\textwidth}{!}{
        \begin{tabular}{ccccc}
            \toprule

            \emph{item\_id} & \emph{date} & \emph{source\_id} \\\midrule

            1 & 2021-01-08 22:08:39 & 9  \\
            2 & 2021-01-09 10:28:58 & 5  \\
            3 & 2021-01-09 14:20:34 & 12 \\
            \vdots & \vdots & \vdots  \\\bottomrule

         \hline
        \end{tabular}
        % }

        \caption{news metadata}
        \label{tab:meta}
    \end{table}

    \begin{itemize}
        \item \emph{source\_id}: source of news item
    \end{itemize}

    \subsection*{content}

    \begin{table}[h]
        \centering
        \resizebox{\textwidth}{!}{
        \begin{tabular}{cll}    \toprule

            \emph{item\_id} &  \emph{news title} & \emph{news content} \\\midrule

        1  &  Azerbaijan denies reports on construction of Turkish air bases in the country & Information that Turkey will create air bases ...        \\
        2  &  Durov announced the massive transition of WhatsApp users to Telegram          & Telegram developer Pavel Durov said in his channel ...   \\
        3  &  Passenger plane that disappeared from radar crashed                           & Passenger plane taking off from Jakarta, disappeared ... \\
        \vdots & \vdots & \vdots \\\bottomrule

         \hline
        \end{tabular}
        }

        \caption{news item}
        \label{tab:item}
    \end{table}

    \subsection*{shows \& views}

    \begin{table}[h]
        \parbox{.45\textwidth}{
            \centering
            \begin{tabular}{ccc}
                \toprule

                \emph{user\_id} & \emph{item\_id} \\\midrule
                10 & 1  \\
                10 & 2  \\
                23 & 1  \\
                23 & 3  \\
                23 & 2  \\
                38 & 3  \\
                38 & 1  \\
                \vdots & \vdots  \\\bottomrule
            \end{tabular}
            \caption{news shows}
            \label{tab:shows}
        }
        \hfill
        \parbox{.45\textwidth}{
            \centering
            \begin{tabular}{ccc}
                \toprule

                \emph{user\_id} & \emph{item\_id} \\\midrule
                10 & 1  \\
                10 & 2  \\
                23 & 1  \\
                38 & 3  \\
                \vdots & \vdots  \\\bottomrule
            \end{tabular}
            \caption{news views}
            \label{tab:views}
            }
    \end{table}

    \begin{itemize}
        \item \emph{shows}: if \emph{item\_id} was shown to the \emph{user\_id}
        \item \emph{views}: if \emph{item\_id} was clicked by the \emph{user\_id}
    \end{itemize}

    \newpage

    \subsection*{emotions \& comments}

    There is an option to react on item via leaving emotion and/or writing a comment.

    \begin{table}[h]
        \parbox{.45\textwidth}{
            \centering
            \begin{tabular}{ccc}
                \toprule

                \emph{user\_id} & \emph{item\_id} & \emph{emotion\_id} \\\midrule
                10 & 1 & 1  \\
                10 & 2 & 3        \\
                23 & 1 & 3        \\
                38 & 3 & 2        \\
                \vdots & \vdots & \vdots  \\\bottomrule

            \end{tabular}
            \caption{users' emotions}
            \label{tab:emotion}
        }
        \hfill
        \parbox{.45\textwidth}{
            \centering
            \resizebox{0.45\textwidth}{!}{
            \begin{tabular}{ccc}
                \toprule

                \emph{user\_id} & \emph{item\_id} & \emph{comment} \\\midrule
                10 & 1 & that's great  \\
                10 & 1 & wish it will continue        \\
                23 & 2 & whatsapp is not competetive anymore        \\
                \vdots & \vdots & \vdots  \\\bottomrule

            \end{tabular}
        }
            \caption{users' comments}
            \label{tab:comment}
            }
    \end{table}

    \begin{itemize}
        \item \emph{emotion\_id}: one of \{{\DejaSans 😄, 😲, 😞, 😡, ♥ }\}
    \end{itemize}

    % \FloatBarrier

    \subsection*{users' subscriptions}

    If \emph{user\_id} subscribed to the \emph{source\_id}.

    \begin{table}[h]
        \centering
        \begin{tabular}{cc}
            \toprule

            \emph{user\_id} & \emph{source\_id} \\\midrule

            10 & 9  \\
            23 & 5  \\
            \vdots & \vdots  \\\bottomrule

        \end{tabular}

        \caption{users' subscriptions}
        \label{tab:subscriptions}
    \end{table}

@@

    \subsection{Popularity-based recommendation}

    We are able to aggreage number of comments and emotions to measure popularity.

    For measuring news item popularity views \& show can be aggregated from tables (cite tables) into:

    \begin{table}[h]
        \centering
        % \resizebox{\textwidth}{!}{
        \begin{tabular}{ccccc}
            \toprule

            \emph{item\_id} & \emph{date} & \emph{source\_id} & \emph{shows}                                                               & \emph{views}                                                 \\\midrule

        1 & 2021-01-08 22:08:39 & 9  & 1043 & 231        \\
        2 & 2021-01-09 10:28:58 & 5  & 828 & 478  \\
        3 & 2021-01-09 14:20:34 & 12 & 163 & 25 \\
        \vdots & \vdots & \vdots & \vdots & \vdots \\\bottomrule

         \hline
        \end{tabular}
        % }

        \caption{news metadata}
        \label{tab:meta}
    \end{table}
